Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-09-28 paper/paper.tex
Tweak slightly

@@

?? Presenting the ultimate big data subgraph matching algorithm is outwith the scope of this paper.

?? We need optimisations for trivial cases. Lazy forward checking, cheap alternatives to heuristics and
all-different. Presolving. Huge domains. Ongoing use of VF2 and micro vs millisecond benchmarks.
Precalculating NDS, distance 2 etc, not for indexing. Edge labels.

@@

@@

>>>>

?? We call these \emph{spuriously hard} instances, to distinguish them from \emph{really hard}
problems. Not the same as \emph{exceptionally hard}.

@@

?? We are not presenting the ultimate big data subgraph matching algorithm.

?? We need optimisations for trivial cases. Lazy forward checking, cheap alternatives to heuristics
and all-different. Presolving. Huge domains.  Precalculating NDS, distance 2 etc, not for indexing.
Edge labels.

@@

\section{Spuriously Hard Instances Outwith Graph Databases}

@@

?? Need for better benchmark instances, not running millisecond versus microsecond benchmarks.
